intro

### 2022-06-02 06_Paper/ER-ED/TheoreticalBackground.Rmd
worked on reviewer 1.1

We assume that people choose the strategy that has the highest value for them at the moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement[@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
The effectiveness of ER strategies should therefore influence the respective SV.
A second, intrinsic, and less obvious goal is the avoidance of effort[@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful[@Hull1943].
This relatively consistent finding could be demonstrated in various domains, for example in the area of affective science[@Gonzalez-Garcia2021], in the area of executive functions, decision behaviour and cognitive control.

>>>>

We assume that people choose the strategy that has the highest value for them at the moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement[@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
The effectiveness of ER strategies should therefore influence the respective SV.
A second, intrinsic, and less obvious goal is the avoidance of effort[@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful[@Hull1943].
Cognitive effort avoidance has been reported in many contexts, for example in affective context[@Gonzalez-Garcia2021], the context of decision making[@Kool2010], and executive functions[@Cheval2020], and could even be deescribed as trait-like characteristic[@Kool2014].
